BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2014-03-29 tex/main.tex
Seems pretty final to me
Minor
Done.
Having fun with latexmk and markdown
Add Copyright

\documentclass[draft]{acm_proc_article-sp}
% \documentclass{acm_proc_article-sp}

\usepackage[ruled, vlined]{algorithm2e}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[autostyle=false, style=english]{csquotes}
\usepackage[usenames,dvipsnames]{color}
\usepackage[justification=centering]{caption}
\usepackage[nodayofweek]{datetime}
\usepackage{amssymb}
\usepackage{booktabs}
% \usepackage{microtype}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{gnuplottex}
\usepackage{pifont}
\usepackage{quoting}
\usepackage[hyphens]{url}
\usepackage{sepfootnotes}
\usepackage{setspace}
\usepackage[pdfpagelabels=false]{hyperref}
\usepackage{hypcap}

@@

  \numberofauthors{7}

  \author{
  % 1st. author
  \alignauthor
  Olivier Blanvillain\\
         \affaddr{École Polytechnique Fédérale de Lausanne (EPFL)}\\
         \affaddr{1015 Lausanne, Switzerland}\\
         \email{\href{mailto:olivier.blanvillain@epfl.ch}{olivier.blanvillain@epfl.ch}}
  % 2nd. author
  \alignauthor
  Nikos Kasioumis\\
         \affaddr{European Organization for Nuclear Research (CERN)}\\
         \affaddr{1211 Geneva 23, Switzerland}\\
         \email{\href{mailto:nikos.kasioumis@cern.ch}{nikos.kasioumis@cern.ch}}
  % 3rd. author
  \alignauthor
  Vangelis Banos\\
         \affaddr{Department of Informatics}\\
         \affaddr{Aristotle University of Thessaloniki, Greece}\\
         \email{\href{vmailto:vbanos@gmail.com}{banos@gmail.com}}
  }

  \additionalauthors{Yannis Manolopoulos (Department of Informatics, Aristotle University of Thessaloniki, Greece, {\texttt{manolopo@csd.auth.gr}})}

@@

  \begin{abstract}
    \input{0-abstract.tex}
  \end{abstract}

@@

  \input{algos.tex}
  \input{tables.tex}
  ~\\~\\~\\~\\~\\~\\~\\
  \input{1-intro.tex}
  \input{2-algorithms.tex}
  \input{3-architecture.tex}
  \input{4-evaluation.tex}
  \input{5-related-work.tex}
  \input{6-conclusion-and-future-work.tex}
  \input{7-acknowledgments.tex}

>>>>

% \documentclass[draft]{acm_proc_article-sp}
\documentclass{acm_proc_article-sp}

% Toggle comment this line, the url and the hyperref package
% to generate a PDF/X-1a compliant output.
% \usepackage[x-1a]{pdfx}

\usepackage[ruled, vlined]{algorithm2e}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[autostyle=false, style=english]{csquotes}
\usepackage[usenames,dvipsnames]{color}
\usepackage[justification=centering]{caption}
\usepackage[nodayofweek]{datetime}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{gnuplottex}
\usepackage{pifont}
\usepackage{quoting}
\usepackage{sepfootnotes}
\usepackage{setspace}
\usepackage[hyphens]{url}
\usepackage[pdfpagelabels=false]{hyperref}
\usepackage{hypcap}

@@

  \numberofauthors{3}

  \author{
  % 1st. author
  \alignauthor
  Olivier Blanvillain\\
         \affaddr{École Polytechnique Fédérale de Lausanne (EPFL)}\\
         \affaddr{1015 Lausanne, Switzerland}\\
         \email{\href{mailto:olivier.blanvillain@epfl.ch}{olivier.blanvillain@epfl.ch}}
  % 2nd. author
  \alignauthor
  Nikos Kasioumis\\
         \affaddr{European Organization for Nuclear Research (CERN)}\\
         \affaddr{1211 Geneva 23, Switzerland}\\
         \email{\href{mailto:nikos.kasioumis@cern.ch}{nikos.kasioumis@cern.ch}}
  % 3rd. author
  \alignauthor
  Vangelis Banos\\
         \affaddr{Department of Informatics}\\
         \affaddr{Aristotle University of Thessaloniki, Greece}\\
         \email{\href{mailto:vbanos@gmail.com}{vbanos@gmail.com}}
  }

  \permission{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that that copies bear this notice and the full citation on the first page. To copy otherwise, to republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee.}
  \conferenceinfo{WIMS'14,}{June 2-4, 2014 Thessaloniki, Greece}
  \CopyrightYear{2014}
  \crdata{978-1-4503-2538-7/14/06}
  \global\copyrightetc{Copyright \the\copyrtyr\ ACM \the\acmcopyr\ ...\$15.00.}

@@

  \begin{abstract}
    \input{0-abstract.mdtex}
  \end{abstract}

@@

  \input{algos.tex}
  \input{tables.tex}
  ~\\~\\~\\~\\~\\~\\~\\

  \section{Introduction}
  \label{introduction}
  \input{1-introduction.mdtex}

  \section{Algorithms}
  \label{algorithms}
  \input{2-algorithms.mdtex}

  \section{Architecture}
  \label{architecture}
  \input{3-architecture.mdtex}

  \section{Evaluation}
  \label{evaluation}
  \input{4-evaluation.mdtex}

  \section{Related Work}
  \label{relatedwork}
  \input{5-related-work.mdtex}

  \section{Conclusion and Future Work}
  \label{conclusionandfuturework}
  \input{6-conclusion-and-future-work.mdtex}

  \section{Acknowledgments}
  \label{acknowledgments}
  \input{7-acknowledgments.mdtex}

  \balance
